Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2023-01-15 paper/manuscript.tex
update intro/results
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Effective teaching involves experts and novices dynamically interacting with each other (Byrne \& Rapaport, 2011). First, experts demonstrate what to be acquired and then novices reproduce what the experts demonstrated. During a skill acquisition process, experts regularly monitor novices' actions and intervene by adapting their behaviour to novices' observed abilities (Mermelshtine, 2017). This interactive learning process will be iterated until novices can perform independently without the help of experts. Experts scaffold novices' learning by finding the specific problem of each novice from their unsuccessful attempts and modify their behaviour accordingly (Ugur, Nagai, Celikkanat, \& Oztop, 2015; Zukow-Goldring \& Arbib, 2007).

Exaggeration of movement is often used to signal a communicative intent to others during real-time interactions (Pezzulo et al., 2019), including teaching contexts. When mothers were teaching how to use a novel toy to their infants, they tended to demonstrate slowly and produce wide and expansive movements compared to when they were demonstrating to adults (Brand, Baldwin, \& Ashburn, 2002). Such exaggeration was observed not only towards infant learners but also when knowledgeable adults were interacting with adult learners (McEllin, Knoblich, \& Sebanz, 2017). For example, participants demonstrating to a learner how to play a particular melody on a xylophone increased the amplitude of their movements, compared to playing the same melody on their own.

Recent evidence from parent-infant interactions suggests that such pedagogical action modulations are sensitive to the skill level of learners (Fukuyama et al., 2015) In this study, mothers were asked to demonstrate a cup-nesting task to their infants. There were four cups with different colour and size. The mothers showed how to stack and fit the nesting cups so that infants could reproduce the actions by themselves. They found that the mothers dynamically modulated their demonstration according to the infants' object manipulation skills. For example, the mothers exaggerated their movements when their infants failed to produce expected actions whereas the mothers did not produce such exaggeration when their infants did not have the motor skills needed to produce the required actions. To the best of our knowledge, it is unknown whether people teaching skills to adult learners also adjust their demonstrations as a function of the learners' demonstrated skills.

To address this question, in the current study we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on the skill level of the novice learners. In our previous research (Tominaga et al., in press), we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

To have experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists The recordings were made based on the performance data from our previous study (Tominaga et al., in press). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (\emph{Fig \ref{fig:stim}}). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

Evidence from parental scaffolding research suggests that caregivers scaffold infants' learning when the infants failed to produce an expected action (Wood \& Middleton, 1975; Zukow-Goldring \& Arbib, 2007). Therefore, we hypothesised that expert pianists would exaggerate their performance only when specific techniques (i.e., either articulation or dynamics, or both) were missing in the recordings. More precisely, expert pianists would exaggerate articulation (i.e., producing longer legato and shorter staccato) when articulation was not implemented in the recordings whereas expert pianists would exaggerate dynamics (i.e., producing louder forte and softer piano, and larger contrast between forte and piano) when dynamics was not implemented in the recordings. If both articulation and dynamics were missing, we predicted that expert pianists would exaggerate both aspects.

@@

As predicted, there was a significant main effect of Articulation (\emph{F}(1, 19) = 5.59, \emph{p} = 0.029, \(\eta_G^2\) = 0.002). There was no significant main effect of Dynamics (\emph{F}(1, 19) = 0.06, \emph{p} = 0.81, \(\eta_G^2\) = 0.000) and no significant interaction between Articulation and Dynamics (\emph{F}(1, 19) = 1.89, \emph{p} = 0.19, \(\eta_G^2\) = 0.002). Participants produced longer legato when listening to the recordings where articulation was not implemented (\emph{Fig \ref{fig:kot-1}}, left).

@@

In line with our prediction, there was a significant main effect of Articulation (\emph{F}(1, 19) = 4.88, \emph{p} = 0.040, \(\eta_G^2\) = 0.009). There was no significant main effect of Dynamics (\emph{F}(1, 19) = 0.68, \emph{p} = 0.42, \(\eta_G^2\) = 0.000) and no significant interaction between Articulation and Dynamics (\emph{F}(1, 19) = 3.13, \emph{p} = 0.093, \(\eta_G^2\) = 0.001). Participants produced shorter staccato when listening to the recordings where articulation was not implemented (\emph{Fig \ref{fig:kot-1}}, right).

@@

Neither the main effect of Articulation (\emph{F}(1, 19) = 1.66, \emph{p} = 0.213, \(\eta_G^2\) = 0.00) nor the main effect of Dynamics (\emph{F}(1, 19) = 0.33, \emph{p} = 0.57, \(\eta_G^2\) = 0.000) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 0.00, \emph{p} = 0.96, \(\eta_G^2\) = 0.000). Participants did not change their performances in terms of notated forte depending on the type of recordings (\emph{Fig \ref{fig:vel-1}}, left).

@@

There was a significant main effect of Articulation (\emph{F}(1, 19) = 7.18, \emph{p} = 0.01, \(\eta_G^2\) = 0.060). However, there was no significant main effect of Dynamics (\emph{F}(1, 19) = 1.80, \emph{p} = 0.20, \(\eta_G^2\) = 0.003) and no significant interaction between Articulation and Dynamics (\emph{F}(1, 19) = 0.04, \emph{p} = 0.85, \(\eta_G^2\) = 0.000). Participants produced softer piano when listening to the recordings where articulation was implemented (\emph{Fig \ref{fig:vel-1}}, right).

@@

@@

These results indicated that participants did not change their performances in terms of dynamics contrast depending on the type of recordings (\emph{Fig \ref{fig:vel-diff-1}}).

@@

Neither the main effect of Articulation (\emph{F}(1, 19) = 2.79, \emph{p} = 0.111, \(\eta_G^2\) = 0.010) nor the main effect of Dynamics (\emph{F}(1, 19) = 3.27, \emph{p} = 0.086, \(\eta_G^2\) = 0.003) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 1.48, \emph{p} = 0.24, \(\eta_G^2\) = 0.002). This indicates that participants did not change the tempo depending on the type of recordings (\emph{Fig \ref{fig:ioi-1}}).

@@

The reason why expert pianists seemed to prioritise the teaching of articulation might be that articulation was more important for the specific piece we selected or the piece itself naturally invited some implementation of articulation. In our previous study, we observed most participants implemented articulation (particularly legato) when they were asked to perform the piece even when neither of articulation nor dynamics was notated on the sheet music. Therefore, it is possible that expert pianists were particularly sensitive to the lack of articulation in the recordings and trying to highlight it. Another possibility is that dynamics modulations in the recordings were too subtle to be noticed by participants and therefore they did not modulate the dynamics aspect of their performance.

We also found that expert pianists did not modulate their tempo (IOIs) depending on the displayed skill levels of students. Also compared with the tempo of the baseline performance (see \emph{Supplementary Material}), they did not change the tempo in the teaching context. These findings indicated that tempo was not employed specifically teaching, likely because tempo itself was not relevant to neither articulation nor dynamics. Although slower demonstration is generally considered to be used for teaching (Brand et al., 2002; McEllin et al., 2017; Schaik, Meyer, Ham, \& Hunnius, 2019), specially in music performance, it may not be an effective strategy to perform slowly as changing the tempo might give another interpretation to the music.

@@

@@

Artificial recordings were generated from performance data that we obtained in our previous study (Tominaga et al.~, in press). We used the data from Experiment 2. In Experiment 2, participants were asked to memorise one piece of music (\emph{Fig 5} (A), Tominaga et al., in press) without any expressive notation before coming to the experiment. First, we asked participants to perform the memorised piece before starting the experiment to measure their baseline performance. After measuring the baseline performance, participants were asked to perform the piece with either articulation (\emph{Fig 5} (B), Tominaga et al., in press) or dynamics (\emph{Fig 5} (C), Tominaga et al., in press) in two conditions (teaching vs.~performing). Here, we only used the data from the performing condition to make sure that performances that we used did not have any particular modulations because of teaching intentions. Therefore, there were two types of performance data (articulation performance: performances played with notated articulation, dynamics performance: performances played with notated dynamics). We obtained 31 valid performances (i.g., performances without pitch errors) as baseline performances, 137 valid performances as articulation performances and 139 valid performances as dynamics performances.

@@

We aimed to generate four types of recordings and each type (i.e., both, art only, dyn only, none) had four instances (see \emph{Apparatus and stimuli}) by using the performance data from Tominaga. First, 16 instances for each type were generated. Second, for each type, we chose the four best instances, which exhibited the characteristic of each type well.

@@

In order to create recordings, we need information about 1) the pitch order, 2) when each note was pressed (related to tempo), 3) when each note was released (related to articulation) and 4) how fast each note was hit. Pitch information was already determined and the same for all structures because of the sheet music (\emph{Fig \ref{fig:stim}}).

First, we created 16 basic structures of recordings from the baseline performances. To determine the temporal information of each structure (i.e., when each key was pressed), three performances out of the 31 valid baseline performances were randomly selected and interonset intervals (IOIs) of the three performances were averaged. Due to the size of the dataset (i.e., 31 performances), some baseline performances were used twice. We made sure that the identical performance was not selected within each random selection (i.e., each selection consisted of three different performances). Thus, we created 16 basic structures for tempi.

Next, we were going to follow the same procedure to determine the sound duration (i.e., when each key was released) of each note (related to articulation) and the key velocity profile (i.e., how fast each key was hit) of each note (related to dynamics). For the sound duration, however, we found that most participants implemented articulation (particularly legato) even in their baseline performances, where they should not implement any particular articulation or dynamics. Therefore, we decided to use the data from only two participants who did not show such tendencies. We obtained four performances from the two participants and used these four performances four times each without performing any averaging so as to have 16 instances in total. For the key velocity profiles, we followed the same procedure as determining tempi and three performances out of the 31 valid baseline performances were randomly selected and key velocity profiles of the three performances were averaged. This is how we created 16 instances for three performance features (i.e., tempo, articulation and dynamics). We generated the 16 recordings where neither articulation nor dynamics was implemented (i.e., none) by combining the three performance features.

@@

There was a significant main effect of Category (\emph{F}(1.79, 34.09) = 5.68, \emph{p} = 0.009, \(\eta_G^2\) = 0.072; Greenhouse-Geisser corrected). Post-hoc comparisons based on the estimated marginal means with Tukey adjustment showed that there were differences between baseline and the other two categories (baseline and both: \emph{p} = .05 , baseline and articulation-only: \emph{p} = .03), suggesting that participants produced softer piano when they had the intention to teach (\emph{Fig \ref{fig:vel-2}}, right).

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-vel-diff-2-1} \caption{\label{fig:vel-diff-2}Comparison with the baseline performance in terms of KV Difference (-127-127) for each subcomponent; forte to piano (left) and piano to forte (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-vel-diff-2}
\end{figure}
\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-ioi-2-1} \caption{\label{fig:ioi-2}Comparison with the baseline performance in terms of IOIs (ms). A dashed line represents the tempo given by a metronome. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-ioi-2}
\end{figure}

>>>>

Effective teaching involves experts and novices dynamically interacting with each other (Byrne \& Rapaport, 2011). First, experts demonstrate what novices are meant to acquired and then novices attempt to reproduce what the experts demonstrated. During a skill acquisition process, experts regularly monitor novices' actions and intervene by adapting their behaviour to novices' observed abilities (Mermelshtine, 2017). This interactive learning process will be iterated until novices can perform independently without the help of experts. Experts scaffold novices' learning by identifying novices' specific problems of each novice from their unsuccessful attempts and modifying their behaviour accordingly (Ugur, Nagai, Celikkanat, \& Oztop, 2015; Zukow-Goldring \& Arbib, 2007).

Exaggeration of movement is often used to signal a communicative intent to others during real-time interactions (Pezzulo et al., 2019), including teaching contexts. When mothers were teaching how to use a novel toy to their infants, they tended to demonstrate slowly and produce wide and expansive movements compared to when they were demonstrating to adults (Brand, Baldwin, \& Ashburn, 2002).Such pedagogical action modulations are sensitive to the skill level of learners. For instance, evidence from parental scaffolding research suggests that caregivers scaffold infants' learning when the infants failed to produce an expected action (Wood \& Middleton, 1975; Zukow-Goldring \& Arbib, 2007). Fukuyama et al. (2015) performed a study, where mothers were asked to demonstrate a cup-nesting task to their infants. There were four cups of different colours and sizes. Mothers demonstrated how to stack and fit the nesting cups with the intention to teach their infants to reproduce the actions by themselves. It was found that the mothers dynamically modulated their demonstrations according to the infants' object manipulation skills. Specifically, mothers exaggerated their movements when their infants failed to produce expected actions but did not produce such exaggerations when their infants lacked the motor skills needed to produce the required actions. Movement exaggerations for the purpose of teaching are observed not only towards infant learners but also when knowledgeable adults are interacting with adult learners (McEllin, Knoblich, \& Sebanz, 2017). For example, participants demonstrating to a learner how to play a particular melody on a xylophone increased the amplitude of their movements, compared to playing the same melody on their own. However, it has not been established whether and how experts teaching skills to adult learners adjust their demonstrations as a function of the learners' demonstrated skills.

To address this question, we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on the skill level of the novice learners. In our previous research (Tominaga, Knoblich, \& Sebanz, 2022), we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question of whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

To gain experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists. The recordings were made based on the performance data from our previous study (Tominaga et al., in press). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (\emph{Fig \ref{fig:stim}}). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

We hypothesised that expert pianists would exaggerate their performance only when specific techniques (i.e., either articulation or dynamics, or both) were missing in the recordings. More precisely, expert pianists would exaggerate articulation (i.e., producing longer legato and shorter staccato) when articulation was not implemented in the recordings whereas expert pianists would exaggerate dynamics (i.e., producing louder forte and softer piano, and larger contrast between forte and piano) when dynamics was not implemented in the recordings. If both articulation and dynamics were missing, we predicted that expert pianists would exaggerate both aspects.

@@

As predicted, experts produced longer legato when listening to the recordings where articulation was not implemented (\emph{Fig \ref{fig:kot-1}}, left). Accordingly, here was a significant main effect of Articulation (\emph{F}(1, 19) = 5.59, \emph{p} = 0.029, \(\eta_G^2\) = 0.002). There was no significant main effect of Dynamics (\emph{F}(1, 19) = 0.06, \emph{p} = 0.81, \(\eta_G^2\) = 0.000) and no significant interaction between Articulation and Dynamics (\emph{F}(1, 19) = 1.89, \emph{p} = 0.19, \(\eta_G^2\) = 0.002).

@@

In line with our prediction, experts produced shorter staccato when listening to the recordings where articulation was not implemented (\emph{Fig \ref{fig:kot-1}}, right). Accordingly, there was a significant main effect of Articulation (\emph{F}(1, 19) = 4.88, \emph{p} = 0.040, \(\eta_G^2\) = 0.009). There was no significant main effect of Dynamics (\emph{F}(1, 19) = 0.68, \emph{p} = 0.42, \(\eta_G^2\) = 0.000) and no significant interaction between Articulation and Dynamics (\emph{F}(1, 19) = 3.13, \emph{p} = 0.093, \(\eta_G^2\) = 0.001).

@@

Unlike our prediction, experts did not change their performances in terms of notated forte depending on the type of recordings (\emph{Fig \ref{fig:vel-1}}, left). Neither the main effect of Articulation (\emph{F}(1, 19) = 1.66, \emph{p} = 0.213, \(\eta_G^2\) = 0.00) nor the main effect of Dynamics (\emph{F}(1, 19) = 0.33, \emph{p} = 0.57, \(\eta_G^2\) = 0.000) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 0.00, \emph{p} = 0.96, \(\eta_G^2\) = 0.000).

@@

Experts produced softer piano only when listening to the recordings where articulation was implemented (\emph{Fig \ref{fig:vel-1}}, right). There was a significant main effect of Articulation (\emph{F}(1, 19) = 7.18, \emph{p} = 0.01, \(\eta_G^2\) = 0.060). However, there was no significant main effect of Dynamics (\emph{F}(1, 19) = 1.80, \emph{p} = 0.20, \(\eta_G^2\) = 0.003) and no significant interaction between Articulation and Dynamics (\emph{F}(1, 19) = 0.04, \emph{p} = 0.85, \(\eta_G^2\) = 0.000).

@@

Unlike our prediction, experts did not change their performances in terms of dynamics contrast depending on the type of recordings (\emph{Fig \ref{fig:vel-diff-1}}).

@@

@@

Unlike our prediction, experts did not change the tempo depending on the type of recordings (\emph{Fig \ref{fig:ioi-1}}). Neither the main effect of Articulation (\emph{F}(1, 19) = 2.79, \emph{p} = 0.111, \(\eta_G^2\) = 0.010) nor the main effect of Dynamics (\emph{F}(1, 19) = 3.27, \emph{p} = 0.086, \(\eta_G^2\) = 0.003) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 1.48, \emph{p} = 0.24, \(\eta_G^2\) = 0.002).

@@

The reason why expert pianists seemed to prioritise the teaching of articulation might be that articulation was more important for the specific piece we selected or that the piece itself naturally invited some implementation of articulation. In our previous study, we observed most participants implemented articulation (particularly legato) when they were asked to perform the piece even when neither articulation nor dynamics was notated on the sheet music. Therefore, it is possible that expert pianists were particularly sensitive to the lack of articulation in the recordings and trying to highlight it. Another possibility is that dynamics modulations in the recordings were too subtle to be noticed by participants and therefore they did not modulate the dynamics aspect of their performance.

We also found that expert pianists did not modulate their tempo (IOIs) depending on the displayed skill level of students. Also compared with the tempo of the baseline performance (see \emph{Supplementary Material}), they did not change the tempo in the teaching context. These findings indicated that tempo was not employed specifically in teaching, likely because tempo itself was not relevant to either articulation or dynamics. Although slower demonstration is generally considered to be used for teaching (Brand et al., 2002; McEllin et al., 2017; Schaik, Meyer, Ham, \& Hunnius, 2019), in music performance, it may not be an effective strategy to perform slowly as changing the tempo might give another interpretation to the music.

@@

\leavevmode\vadjust pre{\hypertarget{ref-tominaga_2022}{}}%
Tominaga, A., Knoblich, G., \& Sebanz, N. (2022). Expert pianists make specific exaggerations for teaching. \emph{Scientific Reports}, \emph{12}(1), 21296. \url{https://doi.org/10.1038/s41598-022-25711-3}

@@

Artificial recordings were generated from performance data that we obtained in our previous study (Tominaga et al., in press). We used the data from Experiment 2. In Experiment 2, participants were asked to memorise one piece of music (\emph{Fig 5} (A), Tominaga et al., in press) without any expressive notation before coming to the experiment. First, we asked participants to perform the memorised piece before starting the experiment to measure their baseline performance. After measuring the baseline performance, participants were asked to perform the piece with either articulation (\emph{Fig 5} (B), Tominaga et al., in press) or dynamics (\emph{Fig 5} (C), Tominaga et al., in press) in two conditions (teaching vs.~performing). Here, we only used the data from the performing condition to make sure that the performances that we used did not have any particular modulations because of teaching intentions. Therefore, there were two types of performance data (articulation performance: performances played with notated articulation, dynamics performance: performances played with notated dynamics). We obtained 31 valid performances (i.g., performances without pitch errors) as baseline performances, 137 valid performances as articulation performances and 139 valid performances as dynamics performances.

@@

We aimed to generate four types of recordings and each type (i.e., both, art only, dyn only, none) had four instances (see \emph{Apparatus and stimuli}) by using the performance data from Tominaga et al (in press). First, 16 instances for each type were generated. Second, for each type, we chose the four best instances, which exhibited the characteristic of each type well.

@@

In order to create recordings, we needed information about 1) the pitch order, 2) when each note was pressed (related to tempo), 3) when each note was released (related to articulation) and 4) how fast each note was hit (related to dynamics). Pitch information was already determined and the same for all structures because of the sheet music (\emph{Fig \ref{fig:stim}}).

First, we created 16 basic structures of recordings from the baseline performances. To determine the temporal feature of each structure (i.e., when each key was pressed), three performances out of the 31 valid baseline performances were randomly selected and interonset intervals (IOIs) of the three performances were averaged. Due to the size of the dataset (i.e., 31 performances), some baseline performances were used twice. We made sure that the identical performance was not selected within each random selection (i.e., each selection consisted of three different performances). Thus, we created 16 basic structures for tempi.

Next, we were going to follow the same procedure to determine the sound duration (i.e., when each key was released) of each note (related to articulation) and the key velocity profile (i.e., how fast each key was hit) of each note (related to dynamics). For the sound duration, however, we found that most participants implemented articulation (particularly legato) even in their baseline performances, where they should not implement any particular articulation or dynamics. Therefore, we decided to use the data from only two participants who did not show such tendencies. We obtained four performances from the two participants and used these four performances four times each without performing any averaging so as to have 16 instances in total. For the key velocity profiles, we followed the same procedure as we determined tempi and three performances out of the 31 valid baseline performances were randomly selected and the key velocity profiles of the three performances were averaged. This is how we created 16 instances for three performance features (i.e., tempo, articulation and dynamics). We generated the 16 recordings where neither articulation nor dynamics was implemented (i.e., none) by combining the three performance features made from the baseline performances.

@@

There was a significant main effect of Category (\emph{F}(1.79, 34.09) = 5.68, \emph{p} = 0.009, \(\eta_G^2\) = 0.072; Greenhouse-Geisser corrected). Post-hoc comparisons based on the estimated marginal means with Tukey adjustment showed that there were differences between baseline and the other two categories (baseline and both: \emph{p} = .05, baseline and articulation-only: \emph{p} = .03), suggesting that participants produced softer piano when they had the intention to teach (\emph{Fig \ref{fig:vel-2}}, right).

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-vel-diff-2-1} \caption{\label{fig:vel-diff-2}Comparison with the baseline performance in terms of KV Difference (-127-127) for each subcomponent; forte to piano (left) and piano to forte (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-vel-diff-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-ioi-2-1} \caption{\label{fig:ioi-2}Comparison with the baseline performance in terms of IOIs (ms). A dashed line represents the tempo given by a metronome. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-ioi-2}
\end{figure}
